Stateless Model Checking with Data-Race Preemption Points

### 2015-11-03 pldi-16/di.tex
some di rephrase

{\bf Initial PPs.}
For testing user-space code, we seed the exploration with the four subsets of ``hard-coded'' locking API PPs shown in Figure~\ref{fig:id}.
By extension, these also introduce preemptions on any other sync primitives implemented with mutexes,
such as condvars, semaphores, and r/w locks.

For kernel-level testing, we consider interrupt-disabling to be analogous to locking,
so we also preempt just before {\tt cli} and just after {\tt sti}\footnote{
During data-race detection, {\tt cli}/{\tt sti} are treated as a single global lock,
as {\tt cli}'d memory accesses can still race with others that have interrupts on.}.
% FIXME: "What happened to yield?" "Yield is implicitly included in each subset."
\quicksand~is configured to use the subsets
$\{ \}$,
$\{lock\}$,
$\{unlock\}$,
$\{cli\}$,
$\{sti\}$,
and $\{lock,unlock,cli,sti\}$.
Other subsets are obviously possible, but as a heuristic, we don't bother with them.

>>>>

{\bf Initial PPs.}
For testing user-space code, we seed the exploration with the four subsets of ``hard-coded'' locking API PPs shown in Figure~\ref{fig:id}.
By extension, these also introduce preemptions on any other sync primitives implemented with mutexes,
such as condvars, semaphores, and r/w locks.
Preempting on voluntary switches such as {\tt yield} is necessary for the invariant that only one thread runs between consecutive PPs,
so the {\tt yield} PP is always implicitly enabled.

For kernel-level testing, we consider interrupt-disabling to be analogous to locking,
so (e.g. on x86) we also preempt just before {\tt cli} and just after {\tt sti}\footnote{
During data-race detection, {\tt cli}/{\tt sti} are treated as a single global lock,
as {\tt cli}'d memory accesses can still race with others that have interrupts on.}.
% FIXME: "What happened to yield?" "Yield is implicitly included in each subset."
\quicksand~is configured to begin with the subsets
$\{ \}$,
$\{lock\}$,
$\{unlock\}$,
$\{cli\}$,
$\{sti\}$,
and $\{lock,unlock,cli,sti\}$.
As a heuristic, we don't bother with every intermediate subset such as $\{lock,sti\}$,
which could potentially be improved in future work (\sect{\ref{sec:future}}).
